Efficient implementation of penalized models and their application to genetic risk prediction

### 2018-08-06 paper/draft.tex
now wait review H.

[REFAIRE] In this comparative study, we present a computationally efficient implementation of penalized logistic regression. 
This model can be used to build polygenic risk scores based on very large SNP datasets such as the UK biobank \cite[]{bycroft2017genome}. 
In agreement with previous work \cite[]{abraham2013performance}, we show that jointly estimating SNP effects has the potential to substantially improve predictive performance as compared to the standard C+T approach in which SNP effects are learned independently. Penalized logistic regression consistently outperform the C+T method, except in the case where there are only small effects and sample size is limited, in which case all methods perform poorly.

>>>>

In this comparative study, we present a computationally efficient implementation of penalized logistic regression. 
This model can be used to build polygenic risk scores based on very large SNP datasets such as the UK biobank \cite[]{bycroft2017genome}. 
In agreement with previous work \cite[]{abraham2013performance}, we show that jointly estimating SNP effects has the potential to substantially improve predictive performance as compared to the standard C+T approach in which SNP effects are learned independently. Penalized logistic regression nearly always outperform the C+T method, and the benefits of using it are stronger with an increasing sample size or when causal SNPs are correlated with one another.
